Radio Sources in the Serpens South Protocluster

### 2014-12-12 Paper/paper.tex
modified:   IRAM_sources.txt 	modified:   Make_Figs.py 	new file:   Paper/deluxetable.sty 	new file:   Paper/emulateapj.cls 	modified:   Paper/figures/SerpSouth_fov_contour-eps-converted-to.pdf 	modified:   Paper/figures/SerpSouth_zoom_color_contour-eps-converted-to.pdf 	modified:   Paper/figures/SerpSouth_zoom_contour-eps-converted-to.pdf 	new file:   Paper/mn2e.cls 	modified:   Paper/paper.pdf 	modified:   Paper/paper.tex 	modified:   Paper/references.bib 	modified:   Rodriguez10_VLA_Sources.reg 	modified:   SERPS_SED.py 	modified:   git_add.sh

%% Document Preamble
% Packages
\usepackage{graphicx}	% Graphics
\usepackage{natbib}		% Bibliography
\usepackage{amsmath}	% Equations
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}		% References
\renewcommand*{\backref}[1]{[#1]}	
\usepackage[all]{hypcap}	% Workaround for hyperref
\usepackage{cleveref}		% Better than autoref
\usepackage{indentfirst}	
\usepackage{fancyhdr}	% Header and Footer
\usepackage{amssymb}	% More symbols
%\usepackage{stfloats}		% For Figures on bottom of page

%% Begin Document
\begin{document}
%\submitted{Submitted: \today}
\title{Radio Properties of Protostars in the Serpens South Protocluster}
\author{Authors}

@@

	Serpens South is a young stellar cluster that is apart of the broader Aquila Rift extinction feature. It lies south of the Serpens Main cloud, and is just West of the bright W40 HII region. Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars, suggesting it is in a very early phase of cluster formation. Since its discovery, it has become the center of a wide range of scholarship. This has consisted of near, mid and far infrared mappings with Spitzer and Herschel tracing heated dust around protostars \citep{Gutermuth08, Bontemps10}, millimeter mappings with MAMBO on the IRAM 30-meter tracing cold dust \citep{Maury11}, near infrared polarimetry revealing the importance of global magnetic fields in the cluster's formation history \citep{Sugitani11}, molecular outflows studies \citep{Nakamura11, Teixeira12}, and a wealth of spectral line surveys probing filamentary infall \citep{Kirk13, Friesen13, Tanaka13, FernandezLopez14,Nakamura14a}. X-ray studies of Serpens South have yet to be published. To-date, only one radio study of Serpens South has been conducted, which used the VLA in its A configuration in 2011 (Ortiz-Leon et al. in prep), meaning that there has yet to be a radio study of Serpens South since the VLA upgraded its facilities 2012. Beyond this study, further radio studies of Serpens South will be important in understanding the star formation process across the electromagnetic spectrum.

	The VLA has been a proven tool in searching for and detecting radio emission around protostars since the early 1990s \citep[e.g.][]{Curiel89, Anglada98, Reipurth99, Eiroa05, Shirley07, Rodriguez10}. Early radio studies of protostars found an excess of radio emission in comparison to the Lyman-Alpha continuum drop off expected from a normal ZAMS star. Theory and observations have best explained protostellar radio emission as having two components: thermal and non-thermal. Thermal radio emission is generally assumed to be free-free emission created from an HII region. High mass protostars have a high enough internal luminosity to support a compact or ultra-compact HII region, however, low mass protostars do not. HII regions surrounding low-mass protostars are created from thermal jets that shock the material surrounding the protostar. Non-thermal emission around low and high mass protostars is still not clearly understood; it is thought to come from gyrosynchrotron emission or possibly from jets that produce synchrotron emission in their tails.

@@

We observed Serpens South on July 2, 2013, for 1 hour with the EVLA in its C array configuration. The increased bandwidth of the EVLA allowed us to split our C band observation into two subbands centered at 4.75 GHz (6.31 cm) and 7.25 GHz (4.14 cm), with a bandwidth of 1.024 GHz for each subband. We focused on a 3.5 arcsec x 3.5 arcsec region around Serpens South's central filament, with a phase center positioned at $\alpha(\text{J2000})=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta(\text{J2000})=-02^{\circ}02^{'}30.0^{''}$. Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour-long observation.

@@

\subsection{Radio Source Selection}
In choosing our sources, we restrict ourself to a circular region centered on our phase center and extending out to 50\% of the primary beam strength. We choose our sources based on their strength in our 4.1 and 6.3 cm maps, their possible spatial alignment with infrared sources, and by referencing our Sextractor source extracted sample \citep{Bertin96}. We were left with a total of 18 radio sources. We then ran source extractions on these spatial positions over near and far infrared data from the JHK bands of 2MASS, the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel. We used a 2 arcsecond maximum matching tolerance for these extractions. Apertures and adopted corrections are consistent with the HOPS survey \{What source should I cite?\}

Eight of our radio sources have at least one infrared source match from 1.25 $\mu$m to 70 $\mu$m, four of which spatially match Spitzer identified Class I/II protostars within 1 arcsecond. A total of ten out of our 18 sources have signs that indicate they are protostellar in nature. One of our radio sources matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they state as Class 0 and starless. Here, we confirm compact radio emission with a rising spectral index indicative of mixed optically thin and thick free-free emission, which suggests the presence of a compact core.

@@

\

%Centered on Serpens South ($\alpha=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta=-02^{\circ}02^{'}30.0^{''}$, J2000.0), we collected data in the VLA C band, using two spectral windows centered at 6.311 cm and 4.135 cm, each with a bandpass width of 1,024 MHz, with two polarization pairs. Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour long observation time. Flux density and bandpass calibrations were done using observations of quasar 3C 286. We obtained a total of 45 minutes of integration on source. 
%
%The data were manually inspected for radio frequency interference (RFI), and we removed obvious RFI from our visibilities. The data were then reduced using standard reduction techniques in CASA 4.1.0. Artifacts and streaks in our final images are products of incomplete $u-v$ coverage of our point spread function, which was slightly enhanced because we did not receive data from 2 of the 27 antennas in the array during our observation, in addition to the bright HII region to the east of Serpens South, contributing extended source signal to our short baselines. 
%
%The Stokes \emph{I} image was deconvolved multiple times with the CLEAN task \citep{Hogbom74, Clark80}, using natural, robust and uniform weighting, utilizing the Cotton-Schwab algorithm \citep{Schwab84}. We find that the best compromise between noise level and source resolution is achieved with robust weighting \citep{Briggs95}. The deconvolutions that produced the highest signal to noise ratios involved using masks around our protostellar sources. We cleaned our 6.3 and 4.1 cm maps down to a RMS noise level of 18$\mu$Jy and 8$\mu$Jy respectively. Table 1 outlines these observations.
%
%We used a circular CLEANing mask centered on the image phase center with a radial extent of $\sim$3 arcseconds, corresponding to 80\% of primary beam strength at the center. Our short integration time, $\sim$45 minutes, left us with a less than desirable point source function, and we therefore set `psfmode' to `hogbom' in the CLEANing process. 
%
%Two particularly strong radio sources in the northern part of our field of view created psf artifacts that were visible in our dirty maps. In addition to this, and the fact that our protostellar sources are relatively weak, we could not readily distinguish between weak protostar emission and a weak compact artifact. Therefore, instead of masking around individual sources, we used a circular mask around 80\% of primary beam strength during the CLEANing process. We compared the final CLEANed image with our psf to check for remaining psf artifacts, and used Spitzer 3.6 $\mu$m maps to spatially confirm centimeter emission from known Spitzer protostars. For the case where compact emission of seemingly protostellar nature does not spatially match a Spitzer protostar, nor an obvious psf artifact, we use its measured radio spectral index and the calculated random probability that it is a background source to discern whether it is a newly detected protostar.

%We used the Jansky Very Large Array (VLA) to image radio continuum emission coming from the Serpens South cluster, taken on July 2nd, 2013. We focused on RA xxxxx DEC xxxxxx, and were sensitive to an area of xxx square degrees. The array was in the C configuration during the observation, which is the second smallest configuration with a maximum baseline length of 3.4 km. We imaged the cluster in the C band, which spans 4238.0 MHz -- 7762.0 MHz. We broke this bandwidth up into two subbands, the first ranging from 4238.00 MHz -- 5262.00 MHz with the middle at $\lambda=6.311$ cm, and the second ranging from 6738.00 MHz -- 7762.00 MHz with the middle at $\lambda=4.135$ cm.

\begin{figure}[h!]
\label{fig:serpsouth_fov}
\centering
\includegraphics[keepaspectratio=True,scale=.6]{figures/SerpSouth_FOV.eps}
\caption{\small{Herschel SPIRE 350 $\mu$m greyscale image of Serpens South. Blue and red triangles indicate Spitzer identified Class I and Class II protostars respectively. The green box indicates our region of interest with the EVLA.}}
\end{figure}

\begin{figure}[h!]
\label{fig:serpsouth_fov_contour}
\centering
\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_fov_contour.eps}
\caption{\small{ 
}}
\end{figure}

\begin{figure}[h!]
\label{fig:serpsouth_zoom_contour}
\centering
\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_zoom_contour.eps}
\caption{\small{ 
}}
\end{figure}

\begin{figure}[h!]
\label{fig:serpsouth_zoom_color_contour}
\centering
\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_zoom_color_contour.eps}
\caption{\small{ 
}}
\end{figure}

%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
\capstartfalse
\begin{deluxetable*}{lccccccc}%cccc}
\label{tab:radio_properties_table}
\tabletypesize{\footnotesize}
\tablecaption{Radio Properties of VLA Sources}
\tablehead{
	\multicolumn{1}{c}{Source}								&
	\multicolumn{2}{c}{Position$^{a}$}							&
	\multicolumn{1}{c}{$S_{6.3 \text{cm}}\ ^{b}$}				&
	\multicolumn{1}{c}{$S^{\text{peak}}_{6.3 \text{cm}}$}		&
	\multicolumn{1}{c}{$S_{4.1 \text{cm}}$}					&
	\multicolumn{1}{c}{$S^{\text{peak}}_{4.1 \text{cm}}$}		&
	\multicolumn{1}{c}{$\alpha_{\text{radio}}\ ^{c}$}				\\ [.25ex]		
%	\multicolumn{1}{c}{L$_{\text{infrared}}$}				&
%	\multicolumn{1}{c}{L$_{\text{bol}}$}					&
%	\multicolumn{1}{c}{Match?}						&
%	\multicolumn{1}{c}{Evolutionary}					\\ [.25ex]
	\cline{2-3}										\\ [-1.5ex]
	\colhead{}										&
	\colhead{RA}									&
	\colhead{Dec.}									&
	\colhead{($\mu$Jy)}								&
	\colhead{($\mu$Jy beam$^{-1}$)}					&
	\colhead{($\mu$Jy)}								&
	\colhead{($\mu$Jy beam$^{-1}$)}					&
	\colhead{}										
%	\colhead{(L$_{\text{sun}}$)}						&
%	\colhead{(L$_{\text{sun}}$)}						&
%	\colhead{(MM/Hersc/Spitz)}						&
%	\colhead{Stage}								
	}
\startdata

6.31\dotfill		&	1.024	&	4.8 x 3.9	&	13.4	&	11.1	\\[1ex]

4.14\dotfill		&	1.024	&	3.2 x 2.5	&	12.7	&	8.5

\enddata
\tablenotetext{a}{Centers of 2D gaussian fits for sources in 4.1 cm map, quoted in J2000 coordinates.}
\tablenotetext{b}{Flux values from images deconvolved with Briggs weighting, \emph{robust}=0.5 \citep{Briggs95}.}
\tablenotetext{c}{Spectral index of peak flux from 6.3 to 4.1 cm, see \autoref{sec:results} for details on calculation.}

\subsection{VLA 1, 2, 3 and 4}
\label{subsec:vla1_2_3_4}

\subsection{VLA 6, 7 and 8}
\label{subsec:vla6_7_8}

\subsection{VLA 9 to 17}
\label{subsec:vla9_to_17}

\subsection{VLA 5 and 18}
\label{subsec:vla18}

@@

@@

-- What paper should I quote for infrared source extraction photometry analysis?

>>>>

%% Document Preamble
% Packages
\usepackage{graphicx}	% Graphics
\usepackage{natbib}		% Bibliography
\usepackage{amsmath}	% Equations
\usepackage[backref,breaklinks,colorlinks,citecolor=blue]{hyperref}		% References
\renewcommand*{\backref}[1]{[#1]}	
\usepackage[all]{hypcap}	% Workaround for hyperref
\usepackage{cleveref}		% Better than autoref
\usepackage{indentfirst}	
\usepackage{fancyhdr}	% Header and Footer
\usepackage{amssymb}	% More symbols
%\usepackage{stfloats}		% For Figures on bottom of page
\usepackage{rotating}		% Rotated figures

%% Begin Document
\begin{document}
%\submitted{Submitted: \today}
\title{Radio Sources in the Serpens South Protocluster}
\author{Authors}

@@

	Serpens South is a young stellar cluster that is a part of the broader Aquila Rift extinction feature. It lies south of the Serpens Main cloud, and is just West of the bright W40 HII region. Discovered in 2008 by \citet{Gutermuth08} as a part of the Spitzer Space Telescope's Gould Belt Legacy survey, Serpens South has been found to harbor an unusually high ratio of Class I to Class II protostars, suggesting it is in a very early phase of cluster formation. Since its discovery, it has become the center of a wide range of scholarship. This has consisted of near, mid and far infrared mappings with Spitzer and Herschel tracing heated dust around protostars \citep{Gutermuth08, Bontemps10}, millimeter mappings with MAMBO on the IRAM 30-meter tracing cold dust \citep{Maury11}, near infrared polarimetry revealing the importance of global magnetic fields in the cluster's formation history \citep{Sugitani11}, molecular outflows studies \citep{Nakamura11, Teixeira12}, and a wealth of spectral line surveys probing filamentary infall \citep{Kirk13, Friesen13, Tanaka13, FernandezLopez14,Nakamura14a}. X-ray studies of Serpens South have yet to be published. Presently only one radio study of Serpens South has been conducted, which used the VLA in its A configuration in 2011 (Ortiz-Leon et al. in prep). Beyond this study, further radio studies of Serpens South will be important in understanding the star formation process across the electromagnetic spectrum.

	The VLA has been a proven tool in searching for and detecting radio emission around protostars since the early 1990s \citep[e.g.,][]{Curiel89, Anglada98, Reipurth99, Beltran01, Eiroa05, Shirley07, Rodriguez10}. Early radio studies of protostars found an excess of radio emission in comparison to the Lyman-Alpha continuum drop off expected from a normal ZAMS star. Theory and observations have best explained protostellar radio emission as having two components: thermal and non-thermal. Thermal radio emission is generally assumed to be free-free emission created from an HII region. High mass protostars have a high enough internal luminosity to support a compact or ultra-compact HII region, however, low mass protostars do not. HII regions surrounding low-mass protostars are created from thermal jets that shock the material surrounding the protostar. Non-thermal emission around low and high mass protostars is still not clearly understood; it is thought to come from gyrosynchrotron emission or possibly from jets that produce synchrotron emission in their tails.

@@

We observed Serpens South on July 2, 2013, for 1 hour with the EVLA in its C array configuration. The increased bandwidth of the EVLA allowed us to split our C band observation into two subbands centered at 4.75 GHz (6.31 cm) and 7.25 GHz (4.14 cm), with a bandwidth of 1.024 GHz for each subband. We focused on a 3.5 arcsec x 3.5 arcsec region around Serpens South's central filament, with a phase center positioned at $\alpha(\text{J2000})=18^{\text{h}}30^{\text{m}}05.00^{\text{s}}, \delta(\text{J2000})=-02^{\circ}02^{'}30.0^{''}$. Gain calibrations were done by switching to J1804 + 0101 every 10 minutes during our hour-long observation. \autoref{fig:serpsouth_fov} shows Serpens South at 350 micron and outlines our field of view.

\begin{figure}[h!]
\label{fig:serpsouth_fov}
\centering
\includegraphics[keepaspectratio=True,scale=.55]{figures/SerpSouth_FOV.eps}
\caption{\small{Herschel SPIRE 350 $\mu$m greyscale image of Serpens South. Blue and red triangles indicate Spitzer identified Class I and Class II protostars respectively. The green box indicates our region of interest with the EVLA.}}
\end{figure}

@@

%%%%%%%%%%%% Begin Table %%%%%%%%%%%%%%%%
\capstartfalse
\begin{deluxetable*}{lcccccccc}
\label{tab:flux_table}
\tabletypesize{\footnotesize}
\tablecaption{Radio Properties of VLA Sources}
\tablehead{
	\multicolumn{1}{c}{Source}								&
	\multicolumn{1}{c}{RA$^{a}$}								&
	\multicolumn{1}{c}{Decl.$^{a}$}							&
	\multicolumn{1}{c}{$S^{\text{int}}_{6.3 \text{cm}}\ ^{b}$}			&
	\multicolumn{1}{c}{$S^{\text{peak}}_{6.3 \text{cm}}$}				&
	\multicolumn{1}{c}{$S^{\text{int}}_{4.1 \text{cm}}$}				&
	\multicolumn{1}{c}{$S^{\text{peak}}_{4.1 \text{cm}}$}				&
	\multicolumn{1}{c}{$\alpha^{\text{int}}_{\text{radio}}$}				&
	\multicolumn{1}{c}{$\alpha^{\text{peak}}_{\text{radio}}$}				\\ [.25ex]		
%	\multicolumn{1}{c}{L$_{\text{infrared}}$}				&
%	\multicolumn{1}{c}{L$_{\text{bol}}$}					&
%	\multicolumn{1}{c}{Match?}						&
%	\multicolumn{1}{c}{Evolutionary}					\\ [.25ex]
	\colhead{}										&
	\colhead{(J2000)}								&
	\colhead{(J2000)}								&
	\colhead{($\mu$Jy)}								&
	\colhead{($\mu$Jy beam$^{-1}$)}					&
	\colhead{($\mu$Jy)}								&
	\colhead{($\mu$Jy beam$^{-1}$)}					&
	\colhead{}										&
	\colhead{}										
%	\colhead{(L$_{\text{sun}}$)}						&
%	\colhead{(L$_{\text{sun}}$)}						&
%	\colhead{(MM/Hersc/Spitz)}						&
%	\colhead{Stage}								
	}
\startdata

VLA\_1	&	18:30:09.68	&	-02:00:32.8	&	844 $\pm$ 8	&	794	&	749 $\pm$ 6	&	718	&	0.28 $\pm$ 0.01	&	0.24 $\pm$ 0.02\\[1ex]

VLA\_2	&	18:30:04.79	&	-02:00:34.1	&	87 $\pm$ 7	&	72	&	177 $\pm$ 7	&	138	&	-1.67 $\pm$ 0.09	&	-1.55 $\pm$ 0.14\\[1ex]

VLA\_3	&	18:30:02.55	&	-02:00:48.5	&	116 $\pm$ 10	&	87	&	140 $\pm$ 2	&	99	&	-0.46 $\pm$ 0.1	&	-0.3 $\pm$ 0.15\\[1ex]

VLA\_4	&	18:30:01.53	&	-02:00:51.6	&	946 $\pm$ 28	&	515	&	1663 $\pm$ 32	&	1178	&	-1.33 $\pm$ 0.04	&	-1.96 $\pm$ 0.02\\[1ex]

VLA\_5	&	18:30:14.79	&	-02:01:27.3	&	167 $\pm$ 10	&	173	&	106 $\pm$ 5	&	95	&	1.07 $\pm$ 0.08	&	1.41 $\pm$ 0.13\\[1ex]

VLA\_6	&	18:30:06.62	&	-02:01:28.9	&	33 $\pm$ 4	&	56	&	79 $\pm$ 7	&	61	&	-2.04 $\pm$ 0.16	&	-0.22 $\pm$ 0.23\\[1ex]

VLA\_7	&	18:30:05.81	&	-02:01:44.9	&	84 $\pm$ 7	&	63	&	48 $\pm$ 4	&	40	&	1.29 $\pm$ 0.13	&	1.08 $\pm$ 0.31\\[1ex]

VLA\_8	&	18:30:06.89	&	-02:02:11.5	&	50 $\pm$ 6	&	50	&	39 $\pm$ 3	&	46	&	0.55 $\pm$ 0.15	&	0.18 $\pm$ 0.29\\[1ex]

VLA\_9	&	18:30:02.80	&	-02:02:25.3	&	60 $\pm$ 1	&	44	&	66 $\pm$ 1	&	50	&	-0.22 $\pm$ 0.03	&	-0.31 $\pm$ 0.29\\[1ex]

VLA\_10	&	18:30:02.95	&	-02:02:32.2	&	260 $\pm$ 17	&	73	&	287 $\pm$ 6	&	119	&	-0.23 $\pm$ 0.07	&	-1.15 $\pm$ 0.15\\[1ex]

VLA\_11	&	18:30:03.36	&	-02:02:45.8	&	73 $\pm$ 4	&	58	&	38 $\pm$ 2	&	36	&	1.5 $\pm$ 0.09	&	1.14 $\pm$ 0.34\\[1ex]

VLA\_12	&	18:30:04.11	&	-02:03:02.1	&	79 $\pm$ 2	&	58	&	30 $\pm$ 2	&	24	&	2.31 $\pm$ 0.09	&	2.06 $\pm$ 0.48\\[1ex]

VLA\_13	&	18:30:03.54	&	-02:03:08.4	&	231 $\pm$ 3	&	227	&	186 $\pm$ 1	&	178	&	0.51 $\pm$ 0.02	&	0.58 $\pm$ 0.07\\[1ex]

VLA\_14	&	18:30:03.84	&	-02:03:12.2	&	83 $\pm$ 2	&	61	&	31 $\pm$ 0	&	37	&	2.29 $\pm$ 0.04	&	1.19 $\pm$ 0.33\\[1ex]

VLA\_15	&	18:30:04.60	&	-02:03:14.1	&	49 $\pm$ 4	&	51	&	68 $\pm$ 1	&	52	&	-0.74 $\pm$ 0.09	&	-0.08 $\pm$ 0.27\\[1ex]

VLA\_16	&	18:30:03.25	&	-02:03:26.6	&	55 $\pm$ 1	&	65	&	63 $\pm$ 2	&	58	&	-0.28 $\pm$ 0.04	&	0.27 $\pm$ 0.23\\[1ex]

VLA\_17	&	18:30:01.32	&	-02:03:42.9	&	161 $\pm$ 4	&	167	&	146 $\pm$ 3	&	135	&	0.22 $\pm$ 0.04	&	0.5 $\pm$ 0.1\\[1ex]

VLA\_18	&	18:30:09.40	&	-02:04:08.8	&	167 $\pm$ 10	&	134	&	170 $\pm$ 3	&	182	&	-0.04 $\pm$ 0.07	&	-0.71 $\pm$ 0.09

\enddata
\tablenotetext{a}{Centers of 2D gaussian fits for sources in 4.1 cm map, quoted in J2000 coordinates.}
\tablenotetext{b}{Flux values from images deconvolved with Briggs weighting, \emph{robust}=0.5 \citep{Briggs95}.}
\tablenotetext{c}{Spectral index of integrated flux from 6.3 to 4.1 cm, see \autoref{sec:results} for details on calculation.}
\tablenotetext{d}{Spectral index of peak flux from 6.3 to 4.1 cm.}
\tablenotetext{e}{}

\subsection{Radio Source Selection}
\label{sec:radio source selection}

In choosing our sources, we restrict ourself to a circular region centered on our phase center and extending out to 50\% of the primary beam strength. We choose our sources based on their strength in our 4.1 and 6.3 cm maps, their possible spatial alignment with infrared sources, and by referencing a source extracted sample using Sextractor \citep{Bertin96}. We were left with a total of 18 radio sources. We then ran source extractions on these spatial positions over the JHK bands of 2MASS, the four IRAC bands of Spitzer, the 24 $\mu$m MIPS band on Spitzer, and the 70 $\mu$m PACS band on Herschel. We used a 2 arcsecond maximum matching tolerance for these extractions. Apertures and adopted corrections are consistent with the HOPS survey.

\begin{figure}[h!]
\label{fig:serpsouth_fov_contour}
\centering
\includegraphics[keepaspectratio=True,scale=.35]{figures/SerpSouth_fov_contour.eps}
\caption{\small{Serpens South radio continuum at 6.3 cm, focused in on green box from \autoref{fig:serpsouth_fov}. Radio contours start at 4$\sigma$ and end at 50$\sigma$. The loose black contour is the same SPIRE 350 $\mu$m contour found in \autoref{fig:serpsouth_fov}. 
}}
\end{figure}

\begin{figure*}
\epsscale{1.15}
\plottwo{figures/SerpSouth_zoom_contour.eps}{figures/SerpSouth_zoom_color_contour.eps}
\caption{{\bfseries Left}: Radio continuum of central filament at 6.3 cm, focused in on red box from \autoref{fig:serpsouth_fov_contour}. Blue and red crosses correspond to Class I and II protostars identified by Spitzer \citep{Gutermuth08}. Green crosses correspond to 1.2 mm dust peaks identified by IRAM \citep{Maury11}. {\bfseries Right}: Identical image as figure on the left, but the background color is PACS 70 $\mu$m image.}
\end{figure*}

Eight of our radio sources have at least one infrared source match from 1.25 $\mu$m to 70 $\mu$m, four of which spatially match Spitzer identified Class I/II protostars within 1 arcsecond. A total of ten out of our 18 sources have signs that indicate they are protostellar in nature. One of our radio sources matches a 1.2 mm source within 1 arcsecond identified by \citep{Maury11}, which they state as starless. Here, we confirm compact radio emission with a rising spectral index indicative of mixed optically thin and thick free-free emission, which suggests the presence of a compact core.

@@

%\subsection{Spectral Indices}
%\label{sec:spix}
%A spectral index is the slope of the flux density in log space between two wavelengths. At radio wavelengths, the spectral index is defined as
%
%\begin{equation}
%\label{eq:radio_spix}
%\alpha_{\text{radio}} = \frac{\ln({S_{\lambda_{1}}/S_{\lambda_{2}})}}{\ln({\lambda_{2}/\lambda_{1}})}
%\end{equation}
%where $\lambda_{2} > \lambda_{1}$ \citep{Shirley07}. Note that we have defined $S_{\lambda}$ in terms of a flux density (e.g. Jansky) not a flux (e.g. $\lambda S_{\lambda}$ or $\nu S_{\nu}$). Theoretical studies have shown that 
%

\subsection{Radio Source Properties}
\label{sec:radio source properties}

\newcommand{\sourcenote}[1]{\textit{#1 ---}}

\sourcenote{VLA 1 - 5}
VLA 1 is relatively isolated from the cluster, has very strong radio emission and has no known protostellar matches in the infrared. These alone would suggest an extragalactic classification, however, it has a slightly rising radio spectral index of 0.28 indicative of optically thin free-free emission. While galaxies are capable of producing  free-free emission from large HII regions, non-thermal synchrotron emission with a steep negative spectral index generally dominates a galaxies' radio emission output. However, because VLA 1 does not spatially match any near or far infrared emission structures, we conclude it is extragalactic in nature.

Sources 2 through 4 seem to be extragalactic. They have no infrared or far-infrared matches and have steep negative radio spectral indices that suggests their emission is non-thermal synchrotron.

VLA 5 is isolated from the cluster and has no infrared or far-infrared matches, but has a strongly rising radio spectral index of 1.41 suggesting that it comes from optically thick free-free emission. Similar to VLA 1, we conclude that it is extragalactic.

@@

The internal luminosity $L_{\text{int}}$ of a protostar is defined as the total luminosity from the protostar and its circumstellar disk if present. The bolometric luminosity of a source can then defined as $L_{\text{bol}}$ = $L_{\text{int}}$ + $L_{\text{ext}}$, where the external luminosity comes from the heated protostellar envelope. It is estimated that $L_{\text{ext}}$ contributes to $L_{\text{bol}}$ on the order of 0.1 $L_{\odot}$ \citet{Dunham08} developed a scaling law relating an embedded protostar's 70 $\mu$m flux to its internal luminosity $L_{\text{int}}$.

@@

-- What paper should I quote for infrared source extraction photometry analysis?\\

-- Do we have to worry about vibrational dust emission in our 4.1 cm data?\\
